camprotR

### 2022-11-08 README.Rmd
Update README

```{r, eval=FALSE}
remotes::install_github("CambridgeCentreForProteomics/camprotR", build_vignettes = TRUE)
```

@@

Several HTML vignettes are installed with this package which go through how to
use different aspects of the package. You can see a list of available vignettes
with:

```{r, eval=FALSE}
browseVignettes("camprotR")
```

>>>>

```{r, eval=FALSE}
remotes::install_github("CambridgeCentreForProteomics/camprotR", dependencies = TRUE)
```

@@

Vignettes which go through how to use different aspects of the package are 
available on the `camprotR` website [here](https://cambridgecentreforproteomics.github.io/camprotR/) (see Articles tab).
